### 2022-12-08 doc/manuscript/translocation.qmd
Test push with fixed typo
Add analysis methods to translocation section

During the period `r min(d1$year)`-`r max(d1$year)`, we conducted `r n_distinct(d1$site_id, d1$date)` translocations of adult frogs to `r n_distinct(d1$site_id)` recipient sites in Yosemite (`r transno_min`-`r transno_max` translocations per site; @fig-yosemap) <!--# Add table of all translocations: site_id, date, frog #s, donor site, etc.? -->. Each translocated cohort included `r transfrogs_min` to `r transfrogs_max` frogs collected from one of `r n_distinct(d1$donor)` donor populations (@fig-yosemap). <!--# #fig-yosemap will likely be moved to supplement -->Estimates of frog survival during the one year following translocation indicate that survival was highly variable between sites, but relatively constant within sites (for the subset of sites that received multiple translocations; @fig-translocation-survival). This suggests an important effect of site characteristics on frog survival. <!--# Add analysis results: translocation_survival_analysis, analysis 2 -->

@@

<!--# Change @fig-survival-postdens from mcmc_areas to mcmc_intervals? Simplify names of predictor variables? -->

@@

Given demographic stochasticity (i.e., probabilistic births and deaths of individuals in a population) and environmental variability in the probability of adult recruitment $\omega$, our model predicted that, following a a single introduction of 40 adult individuals into a population, the six populations with the highest adult survival probabilities had 50-year extinction probabilities of less than 1 (@fig-viability B). Therefore, even under conservative assumptions about recruitment probability $\omega$, these populations had some probability of persistence over 50 years following a single introduction. For these six populations, as $\omega$ increased from 0.1 to 0.3, 50 year extinction probability was less 0.5, indicating strong potential for long-term persistence in the presence of Bd and environmental variability in recruitment success (@fig-viability B). In contrast, for the six populations where $\sigma_{A_R} < 0.5$, extinction probability over 50 years was always predicted to be 1. To test the validity of our model predictions, we demonstrated that our stochastic model could describe the general recovery trajectory of our translocated population with the longest surveillance history (@fig-viability-supp B; population 70550, surveyed for 16 years). <!--# Add information about natural recruitment probability in the study populations? Can we even calculate recruitment probability? -->

@@

![For the best model identifying predictors of 1-year frog survival following translocation, estimated posterior density curves and shaded 95% uncertainty intervals for all predictor variables. Variables are considered important predictors if the associated uncertainty interval does not overlap zero (dashed red line).](figures/mcmc_areas_m1d.png){#fig-survival-postdens}

@@

<!--# Mention sampled declining populations also? -->

@@

##### Estimation of adult survival and population size

@@

@@

To identify important predictors of frog survival following translocation, we developed multilevel models in a Bayesian framework. We performed all analyses using R Statistical Software [v4.4.4; @rsoftware2022] and the rstanarm package [@rstanarm2022]. <!--# Add details and citations, from PeerJ paper? -->

>>>>

During the period `r min(d1$year)`-`r max(d1$year)`, we conducted `r n_distinct(d1$site_id, d1$date)` translocations of adult frogs to `r n_distinct(d1$site_id)` recipient sites in Yosemite (`r transno_min`-`r transno_max` translocations per site; @fig-yosemap). Each translocated cohort included `r transfrogs_min` to `r transfrogs_max` frogs collected from one of `r n_distinct(d1$donor)` donor populations (@fig-yosemap). Estimates of frog survival during the one year following translocation indicate that survival was highly variable between sites, but relatively constant within sites (for the subset of sites that received multiple translocations; @fig-translocation-survival). As such, for sites that received more than one translocation, the average survival of frogs in the first translocation to a site was an important predictor of survival of frogs in all subsequent translocations to that site (median of posterior distribution = 4.14, uncertainty interval = 3.06\--5.28; see Supporting Information for analysis details). The relatively constant within-site frog survival across all translocations suggests an important effect of site characteristics on frog survival. <!--# How to extract these values from table produced by line 934 in translocation_survival_analysis.Rmd? -->

@@

@@

Given demographic stochasticity (i.e., probabilistic births and deaths of individuals in a population) and environmental variability in the probability of adult recruitment $\omega$, our model predicted that, following a a single introduction of 40 adult individuals into a population, the six populations with the highest adult survival probabilities had 50-year extinction probabilities of less than 1 (@fig-viability B). Therefore, even under conservative assumptions about recruitment probability $\omega$, these populations had some probability of persistence over 50 years following a single introduction. For these six populations, as $\omega$ increased from 0.1 to 0.3, 50 year extinction probability was less 0.5, indicating strong potential for long-term persistence in the presence of Bd and environmental variability in recruitment success (@fig-viability B). In contrast, for the six populations where $\sigma_{A_R} < 0.5$, extinction probability over 50 years was always predicted to be 1. To test the validity of our model predictions, we demonstrated that our stochastic model could describe the general recovery trajectory of our translocated population with the longest surveillance history (@fig-viability-supp B; population 70550, surveyed for 16 years). <!--# To help constrain the possible values of omega, add information about recruitment probability  observed in the study populations? Because we don't have accurate counts of subadults, can we even calculate recruitment probability? -->

@@

![For the best model identifying predictors of 1-year frog survival following translocation, estimated posterior density curves and shaded 95% uncertainty intervals for all predictor variables. Variables are considered important predictors if the associated uncertainty interval does not overlap zero (dashed red line). <!--# Change @fig-survival-postdens from mcmc_areas to mcmc_intervals? Simplify names of predictor variables? -->](figures/mcmc_areas_m1d.png){#fig-survival-postdens}

@@

<!--# Mention that we sampled declining populations also? Will need to update map and text to show only the samples that were sequenced. -->

@@

##### Estimation of adult survival and population size from CMR surveys

@@

We estimated survival of translocated frogs, recruitment of new frogs into the adult population, and population size using a Bayesian open-population Jolly-Seber mark-recapture model with known additions (i.e., translocated cohorts) to the population, as implemented by the mrmr package [@joseph2019] and using R Statistical Software [v4.4.4; \@rsoftware2022]. The model tracks the states of *M* individuals that comprise a superpopulation made up of real and pseudo-individuals [see @joseph2018 for details]. The possible states of individuals include "not recruited", "alive", and "dead". The possible observations of individuals include "detected" and "not detected". We assume that individuals that are in the "not recruited" or "dead" states are never detected (i.e., there are no mistakes in the individual PIT tag records). For all models, we used mrmr defaults for priors, number of chains (4), and warmup and post-warmup iterations (2000 for each). We evaluated convergence of the Markov chain Monte Carlo (MCMC) algorithm using trace plots and Gelman-Rubin statistics (Rhat). Code used to construct CMR datasets and fit models for each translocated population is available from a GitHub repository ([https://github.com/SNARL1/cmr-analysis](https://github.com/SNARL1/cmr-analysis.)).

@@

To identify important predictors of frog survival following translocation, we developed multilevel models in a Bayesian framework. We performed all analyses using R Statistical Software [v4.4.4; @rsoftware2022] and the rstanarm package [@rstanarm2022]. We started with models that included all relevant population-level effects and, when data contained possible hierarchical structure, we included group-level effects in the full model. Within each analysis, we evaluated model fit using visualizations of leave-one-out ("LOO") probability integral transformations [@gelman2013, @gabry2019], and compared fits of models with and without group-level effects, and with differing group-level effects using LOO cross-validation [@vehtari2016]. Both approaches utilized the loo package.

Of the two analyses we conducted, one focused on identifying predictors of post-translocation frog survival from a wide range of variables describing characteristics of frogs, habitat, and translocations \[@fig-survival-postdens\]. The other analysis focused specifically on whether survival of frogs in the first translocation to a site predicted the survival of frogs in subsequent translocations. In both analyses, the response variable, probability of frog survival, was rounded to integer values to produce a binomial outcome, and all models used a bernoulli family. For all models, we used default priors, four chains, and 5000 iterations each for warmup and post-warmup. We checked convergence of the MCMC algorithm using trace plots and Rhat. Code to create datasets and fit models is available from the following GitHub repository: <https://github.com/SNARL1/translocation>.
